Sparse Function Space Representation of Neural Networks for Exploration and Representation

### 2023-04-25 paper/main.tex
Reordering things

%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
%\title{Sequential Decision-Making under Uncertainty with Big Data}
% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
\title{Sparse Function Space Representation of Neural Networks for Exploration and Representation}
% \title{Capturing Neural Networks with Gaussian Processes for Sequential Decision-Making Under Uncertainty}

\author{%
  Aidan ~Scannell \\
  Aalto University\\
  %Finnish Center for Artificial Intelligence \\
  \texttt{aidan.scannell@aalto.fi}
  \And
  Paul ~Chang \\
  Aalto University\\
  \texttt{paul.chang@aalto.fi}
  \And
  Ella ~Tamir \\
  Aalto University\\
  \texttt{ella.tamir@aalto.fi}
  \And
  Arno ~Solin \\
  Aalto University\\
  \texttt{arno.solin@aalto.fi}
  \And
  Joni ~Pajarinen \\
  Aalto University\\
  \texttt{joni.pajarinen@aalto.fi}
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

@@

\section{Introduction} \label{sec:intro}

Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime.

>>>>

@@

%\title{Investigatin Uncertainty Quantification in Model-based Reinforcement Learning}
% \title{Model-based Reinforcement Learning with Fast Posterior Updates}
%\title{Sequential Decision-Making under Uncertainty with Big Data}
% \title{Neural Network to Vatiational Sparse Gaussian Process: For Adaptive Exploration}
% \title{Neural Network to Sparse Variational Gaussian Process: For Updates in Sequential Decision Making}
% \title{Adapting Neural Networks to New Data For Updates in Sequential Decision Making via Gaussian Processes}
% \title{Converting Neural Networks to Gaussian Processes for Sequential Decision-Making Under Uncertainty}
\title{Sparse Function Space Representation of Neural Networks for Exploration and Representation}

\author{%
  Aidan Scannell\textsuperscript{\star} \\
  Aalto University \\
  Finnish Center for Artificial Intelligence \\
  \texttt{aidan.scannell@aalto.fi}
  \And
  Riccardo Mereu\textsuperscript{\star} \\
  Aalto University\\
  \texttt{riccardo.mereu@aalto.fi}
  \And
  Paul Chang \\
  Aalto University\\
  \texttt{paul.chang@aalto.fi}
  \And
  Ella Tamir \\
  Aalto University\\
  \texttt{ella.tamir@aalto.fi}
  \And
  Joni Pajarinen \\
  Aalto University\\
  \texttt{joni.pajarinen@aalto.fi}
  \And
  Arno Solin \\
  Aalto University\\
  \texttt{arno.solin@aalto.fi}
}

@@

\section{Introduction}
\label{sec:intro}
%
Neural networks have experienced unparalleled success in the large data, offline and gradient-based training regime. 
Deep learning is great and in the suerpvised and unsupervised setting solve large-scale problems.
How about sequential learning problems such as continual or reinforcement learning.
In continual learning mainitaining a compact representation
